Text Is All You Need

### 2023-05-11 docs/hes_final/presentation.qmd
make bullets of ffnn features

- 2 numerical indicators from UNICEF's State of the World's Children report: 'Under-five mortality rate 2019' & 'Adolescent population 2020 Proportion of total population (%) Total'
- 3 one-hot-encoded categorical indicators: Human Development Index ranges, categories of gross national income per capita, & categories of Fragile States Index ranges)

@@

- Trained using a dataset that drew multiple samples per country per month of 50 articles each 
- This created multiple unique training examples for each country and month 
- Once trained, the Encoder's weights were frozen and penultimate layer was exposed
:::

@@

### The Classifier

@@

::: {.column width="50%"}
- Each country/month embedding matrix was passed into the Encoder in batches of 50 articles
- This produced a single distilled training example for each country and month
- This final, undistorted data set was then used for classification

>>>>

- 2 numerical indicators from UNICEF's State of the World's Children report: 
  + 'Under-five mortality rate 2019' 
  + 'Adolescent population 2020 Proportion of total population (%) Total'
- 3 one-hot-encoded categorical indicators: 
  + Human Development Index ranges 
  + gross national income per capita
  + Fragile States Index ranges

@@

- Trained using a dataset that drew multiple samples per country per month of 50 articles each 
- The same label was used for each subsample, creating multiple unique training examples for each country and month 
- This produced a larger, but more distorted corpus
:::

@@

### Training the Classifier

@@

::: {.column width="50%"}
- Once the Encoder was trained, it's penultimate layer of 16 dense neurons was exposed and the model was frozen
- Each country/month matrix was then fed into in batches of 50 articles, yeilding a single training example for each country and month of size $16\times\frac{n}{50}$
